---
title: "Mixpanel API"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Mixpanel API}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

One of the primary purposes of the `emmytics` package is to access data from Mixpanel. Once you have your credentials setup (see the [Local Setup for Mixpanel API Access](env_setup.html) vignette), you can use `get_mixpanel_data` to query the data.

## Query data

The first thing you'll need to do is load `emmytics` for the API access and `dplyr` for basic munging.

```{r load, message=FALSE, warning=FALSE}
library(dplyr)
library(emmytics)
```

Web analytics data for a number of pilots are stored and accessible from Mixpanel. To access the table of current pilot in Mixpanel and their dates, you can run `pilot_pds`. You can then store one of the pilots start and end dates to use in the api.

```{r pilots}
#see pilot dates
pilot_pds
```

If you were interested in pulling down the data from the Louisiana November 2025, you could grab those dates from the `pilot_pds` table to use in your API.

```{r focal_pilot}
#use the dates from the LA 2025 November pilot
la_2025nov <- pilot_pds %>% 
  filter(state == "LA", pilot == "Nov 2025")

la_2025nov
  
```

You can plug these dates into `get_mixpanel_data` to access and store the Mixpanel data locally in your project's `/Data` folder.

```{r api, eval=FALSE}
#run API & store locally
get_mixpanel_data(
    from_date = la_2025nov$start_date,
    to_date = la_2025nov$end_date,
    client_agency = la_2025nov$client_agency,
    cache_dir = "Data"
    )
```

Running this function will store the data a NDJSON (`Data/mixpanel_data_la_ldh_2025-11-16_to_2025-11-22.json`) for use in your analytics.



