---
title: "Local Setup for Mixpanel API Access"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Setup for API Access}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

In order to use the API to access the EMMY Mixpanel project data, you will need the project keys. This vignette walked you through the process of how to do the initial setup to be able to access the API.

## 1. Outreach

The first step is to reach out to the EMMY project engineers who will be able to provide you withe the shared keys you need for the Mixpanel Production Service Account - username and secret.

## 2. Storage

With the two keys from the project engineers, you'll need to store these in a `.env.local` within your project. To do so, you can run `setup_env_file`, which will create the file template within your project directory and from there you can add each of the keys to their respective lines. This function also add this file to the project's `.gitignore` to avoid errantly committing this file to a public repository.


```{r load, message=FALSE, warning=FALSE}
library(dplyr)
library(emmytics)
```

```{r setup, eval=FALSE}
setup_env_file()
```

Running this function produces a file that looks like the text below. You'll drop in the credentials on their respective lines.

```{file_text}
# ##############################################################################
# This file contains API keys that must be provisioned by each developer as
# part of onboarding.
# ##############################################################################

# ##############################################################################
# Mixpanel analytics keys

MIXPANEL_PROJECT_ID=3511732
MIXPANEL_SERVICE_ACCOUNT_USERNAME=[enter username here]
MIXPANEL_SERVICE_ACCOUNT_SECRET=[enter secret here]
```

Once you have entered in the credentials, save the file. Check your `.gitignore` to ensure that the `env.local` will be ignored.

## 3. Get going

With the credentials stored, you should be good to go. There is a function that loads the Mixpanel service account credentials as environment variables for your session to be accessed during the API call, but this is actually built into the API function so you don't need to manually run this.

```{r load_creds, eval=FALSE}
#quietly load account cres as environemnt variables
load_env() # <- unnecessary step
```

To access the table of current pilot in Mixpanel and their dates, you can run `pilot_pds`. You can then store one of the pilots start and end dates to use in the api.
```{r pilots}
#see pilot dates
pilot_pds

#use the dates from the LA 2025 November pilot
la_2025 <- pilot_pds %>% 
  filter(state == "LA", pilot == "Nov 2025")

la_2025
```

You can plug these dates into `get_mixpanel_data` to acccess and store the Mixpanel data locally.

```{r api, eval=FALSE}
#run API & store locally
get_mixpanel_data(
    from_date = la_2025$start_date,
    to_date = la_2025$start_date$end_date
    )
```






